---
title: "assignment3"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
```

### The space shuttle crashed landed but there were concerns before the flight that they shouldn't fly the shuttle. They didnt do a good job of data visualization and relaying their point so our job is to give god visualization of why they should fly.

```{r}
data.table::fread("./o-ring-erosion-or-blowby.data") -> ring.data

ggplot(ring.data, aes(x = TEMPORDFLIGT, y = THERMALDIS, size = LAUNCHTEMP))+
  geom_point() +
  xlab("Temporal order of flight")+
  ylab("# of O-Rings experiencing thermal distress") +
  ggtitle("Number of O-rings at risk", subtitle = "Number of O-rings that will experience thermal distress for a given flight when the launch temperature is below freezing")

```


### The cause of the disaster was traced to an O-ring, a circular gasket that sealed the right rocket booster. This had failed due to the low temperature (31°F / -0.5°C) at launch time – a risk that several engineers noted, but that NASA management dismissed.

```{r}

ggplot(ring.data, aes(x = LAUNCHTEMP, y = THERMALDIS, size = LAUNCHTEMP))+
  geom_smooth() +
  xlab("Launch Temp")+
  ylab("# of O-Rings experiencing thermal distress") +
  ggtitle("Number of O-rings at risk", subtitle = "Number of O-rings that will experience thermal distress for a given flight when the launch temperature is below freezing")

```

